TestEvol: A Tool for Analyzing Test-Suite Evolution

### 2012-11-03 icse2013demo-testevol/paper.tex

\usepackage{times}
\usepackage{graphicx}
\usepackage{epsfig}
% \usepackage{url}
% \usepackage{hyperref}
\usepackage[bookmarks=false]{hyperref}
\usepackage{xspace}\usepackage{float}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage[usenames]{color}
\usepackage{multirow}
\usepackage{listings}
\usepackage{textcomp}

@@

@@

\begin{abstract}
  Test suites, once created, rarely remain static. Just like the
  application they are testing, they evolve throughout their lifetime.
  Test obsolescence is probably the most known reason for test-suite
  evolution---test cases cease to work because of changes in the code
  and must be suitably repaired. There are several reasons why it is
  important to achieve a thorough understanding of how test cases
  evolve in practice. In particular, researchers who develop automated
  test-repair techniques---an increasingly active research area---can
  use such understanding to develop more effective repair techniques
  that are applicable in real-world scenarios. More generally,
  analyzing test-suite evolution can help testers better understand
  how test cases are modified during maintenance and improve the test
  evolution process, an extremely time consuming activity for any non
  trivial test suite.  Unfortunately, there are no existing tools that
  facilitate investigation of test-suite evolution. To tackle this
  problem, we developed \tool, a tool that enables the systematic
  study of test-suite evolution for Java programs and JUnit test
  cases.  This demonstration presents \tool and demonstrates its
  usefulness and practical applicability by showing how \tool\ can be
  used on real-world software and unit test suites.
\end{abstract}

@@

In our demonstration, we show an implementation of our technique,
\tool, that works for Java programs and JUnit test suites ({\small
  \url{http://www.junit.org/}}). We chose Java and JUnit because the
former is a widely used language, and the latter is the de-facto
standard unit-testing framework for Java.  \tool\ analyzes a sequence
of versions of a software system, where each version consists of
application code and test code and can be an actual release or an
internal build.

\tool\ is implemented as a Java based web application that runs on
Apache Tomcat ({\small \url{http://tomcat.apache.org/}}). Although the
tool can be installed locally, using a local server, users who want to
get familiar with \tool\ without having to install it can access it
remotely on our servers. The tool is currently available at {\small
  \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}}, and
unregistered users can access the tool using account ``icse'', with
password ``icse2013''.

Due to space limitations, we can only provide a few examples of
\tool's graphical interface. The companion video demonstration for
this paper illustrates the tool interface in full detail. Figure...

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{1-summary}
        \vspace*{-16pt}
	\caption{TBD.}
        \vspace*{-8pt}
	\label{fig:summary}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{2-versiondetails}
        \vspace*{-16pt}
	\caption{TBD.}
        \vspace*{-8pt}
	\label{fig:versiondetails}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{3-testdetails}
        \vspace*{-16pt}
	\caption{TBD.}
        \vspace*{-8pt}
	\label{fig:testdetails}
\end{figure}

\tool\ consists of five components, as illustrated in the architecture
diagram shown in Figure~\ref{fig:trex}. 
%
The \emph{compiler} component builds each system version and creates
two jar files, one containing the application classes and the other
containing the test classes.
%
The \emph{test-execution engine} analyzes each pair of system versions
$(S, S')$, where $S = (P, T)$ and $S' = (P', T')$.  First, it executes
$T$ on program $P$ and $T'$ on program $P'$ (\ie it runs the tests on
the respective program versions).  Then, it executes $T'$ on $P$ and
$T$ on $P'$. For each execution, it records the test outcome: $\pass,
\failce, \failae, or \failre$.
%
The \emph{differencing component} compares $T$ and $T'$ to identify
modified, deleted, and added tests. This component is implemented
using the \textsc{wala} analysis infrastructure for Java ({\small
  \url{wala.sourceforge.net}}).

The test outcomes, collected by the test-execution engine, and the
test-suite changes, computed by the differencing component, are then
passed to the \emph{test classifier}, which analyzes the information
about test outcomes and test updates to classify each update into one
of the eight test-evolution categories presented in
Section~\ref{sec:test-evolution}.  For each pair of broken test case
and its repaired version, the test classifier also compares the test
cases to identify the types of repair changes---different types of
method-sequence changes and assertion changes---as discussed in
Section~\ref{sec:category-rep}; this analysis is also implemented
using \textsc{wala}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{architecture}
        \vspace*{-16pt}
	\caption{High-level architecture of \tool.}
        \vspace*{-8pt}
	\label{fig:trex}
\end{figure}

>>>>

\usepackage{times}
\usepackage{graphicx}
\usepackage{epsfig}
% \usepackage{url}
% \usepackage{hyperref}
\usepackage{hyperref}
\usepackage{xspace}\usepackage{float}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage[usenames]{color}
\usepackage{multirow}
\usepackage{listings}
\usepackage{textcomp}

@@

\hypersetup{
colorlinks=true,
bookmarksnumbered=true,
pdftitle={Isolating Failure Causes through Test Case Generation},
pdfauthor={Jeremias R\"o\ss{}ler and Gordon Fraser and Andreas Zeller and Alessandro Orso},
pdfsubject={Automated Testing},
pdfkeywords={Automated Debugging, Diagnostics, Testing tools}
}

@@

\begin{abstract}
  Test suites, once created, rarely remain static. Just like the
  application they are testing, they evolve throughout their lifetime.
  Test obsolescence is probably the most known reason for test-suite
  evolution---test cases cease to work because of changes in the code
  and must be suitably repaired. There are several reasons why it is
  important to achieve a thorough understanding of how test cases
  evolve in practice. In particular, researchers who develop automated
  test-repair techniques---an increasingly active research area---can
  use such understanding to develop more effective repair techniques
  that are applicable in real-world scenarios. More generally,
  analyzing test-suite evolution can help testers better understand
  how test cases are modified during maintenance and improve the test
  evolution process, an extremely time consuming activity for any non
  trivial test suite.  Unfortunately, there are no existing tools that
  facilitate investigation of test-suite evolution. To tackle this
  problem, we developed \tool, a tool that enables the systematic
  study of test-suite evolution for Java programs and JUnit test
  cases.  This demonstration presents \tool and demonstrates its
  usefulness and practical applicability by showing how \tool\ can be
  used on real-world software and unit test suites.

  \noindent
  Demo video at {\small \url{http://www.cc.gatech.edu/~orso/software/testevol/}}

\end{abstract}

@@

In our demonstration, we show an implementation of our technique,
\tool, that works on Java programs and JUnit test suites ({\small
  \url{http://www.junit.org/}}). We chose Java and JUnit because the
former is a widely used language, and the latter is the de-facto
standard unit-testing framework for Java.  \tool\ analyzes a sequence
of versions of a software system, where each version can be an actual
release or an internal build and consists of application code and test
code.

\tool\ is implemented as a Java based web application that runs on
Apache Tomcat ({\small \url{http://tomcat.apache.org/}}). Although the
tool can be installed locally, users who want to get familiar with
\tool\ without having to install it can also access it remotely at
{\small \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}},
specifying user ``icse'' and password ``icse2013''.

Due to space limitations, we can only provide a few examples of
\tool's graphical interface. (The companion demo video illustrates the
tool interface in full detail.) Figure~\ref{fig:summary} shows the
summary report generated by \tool\ for two pairs of versions of
project \subject{google-gson}. The report shows the number of tests,
both total and per version, that fall in each of the eight categories
defined in our approach.  By clicking on a pair of versions, the user
can obtain detailed report for a specific pair of versions. To
illustrate, Figure~\ref{fig:versiondetails} shows the detailed report
for versions $v.1.1$--$v.1.2$ and a specific category of differences
(\catrep). By further clicking on a test case in the list, users can
also inspect, in the case of modified tests, the actual differences
between the two versions of that test, as shown in
Figure~\ref{fig:summary} for test case \subject{TypeInfoTest}.

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{1-summary}
        \vspace*{-20pt}
	\caption{Summary report for two pairs of versions of a
          project.}
        \vspace*{-8pt}
	\label{fig:summary}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{2-versiondetails}
        \vspace*{-20pt}
	\caption{Detailed report for a pair of versions.}
        \vspace*{-8pt}
	\label{fig:versiondetails}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{3-testdetails}
        \vspace*{-20pt}
	\caption{Differences between two versions of a test case.}
        \vspace*{-8pt}
	\label{fig:testdetails}
\end{figure}

In terms of design, \tool\ consists of five components, as illustrated
in Figure~\ref{fig:trex}.
%
The \emph{compiler} component builds each system version and creates
two jar files, one containing the application classes and the other
containing the test classes.
%
The \emph{test-execution engine} analyzes each pair of system versions
$(S, S')$, where $S = (P, T)$ and $S' = (P', T')$.  First, it executes
$T$ on program $P$ and $T'$ on program $P'$ (\ie it runs the tests on
the respective program versions).  Then, it executes $T'$ on $P$ and
$T$ on $P'$. For each execution, it records the test outcome: $\pass,
\failce, \failae, or \failre$.
%
The \emph{differencing component} compares $T$ and $T'$ to identify
modified, deleted, and added tests. This component is implemented
using the \textsc{wala} analysis infrastructure for Java ({\small
  \url{wala.sourceforge.net}}).

The test outcomes, collected by the test-execution engine, and the
test-suite changes, computed by the differencing component, are then
passed to the \emph{test classifier}, which analyzes the information
about test outcomes and test updates to classify each update into one
of the eight test-evolution categories presented in
Section~\ref{sec:test-evolution}. For each pair consisting of a broken
test case and its repaired version, the test classifier also compares
the test cases to identify the types of repair changes---different
types of method-sequence changes and assertion changes---as discussed
in Section~\ref{sec:category-rep}; this analysis is also implemented
using \textsc{wala}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{architecture}
        \vspace*{-20pt}
	\caption{High-level design of \tool.}
        \vspace*{-8pt}
	\label{fig:trex}
\end{figure}
